Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}

### 2013-05-08 article/sigproc-sp.tex
Added back working application section
Updated graphics formats for images not showing. Scaled up fonts in images and resized some images to make them fit better into the article. Added cluster histogram

\begin{figure*}
\centering
\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
\caption{Jaccard Similarity vs. normalized edit distance.}
\label{jac-ed}
\end{figure*}

As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases. Figure \ref{fig:jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$. At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65]. Clearly setting $l$ too high can increase the false positive rate, but setting $l$ too low will increase the false positive rate, since it will increase the size of the intersection of the shingle sets.

@@

\begin{figure*}
\centering
\epsfig{file=edgrid.eps,width=7in}
\caption{}
\label{ed-grid}
\end{figure*}

@@

\begin{center}
\includegraphics[scale=0.43, keepaspectratio = true]{Top10ArticlePairs.jpg}
\end{center}

@@

After performing minhash on all of Wikipedia, we were able to cluster all unique sentences. Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large. What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$. Based on the fact that we found $\approx 6500$ article pairs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common. As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in TOP 10 SIMILARITY COUNTS FIGURE).

>>>>

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
%\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
\caption{Jaccard Similarity vs. normalized edit distance.}
\label{jac-ed}
\end{figure}

As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases. Figure \ref{jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$. At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65]. Clearly setting $l$ too high can increase the false positive rate, but setting $l$ too low will increase the false positive rate, since it will increase the size of the intersection of the shingle sets.

@@

\begin{figure}
\centering
\epsfig{file=edgrid.eps,width=3.5in}
\caption{}
\label{ed-grid}
\end{figure}

\section{Working Application}
\begin{itemize}
\item MinhashWikipediaPages
\item DedupSentences
\item MergeClusters
\item GetSentenceClusters
\item Edit Distance Filter
\end{itemize}

\subsection{Limitations of Approach}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.43, keepaspectratio = true]{Top10ArticlePairs.jpg}
\end{center}
\caption{Top 10 Similarity Counts}
\label{toparticles}
\end{figure}

@@

After performing minhash on all of Wikipedia, we were able to cluster all unique sentences. Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM \ref{clust}, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large. What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$. Based on the fact that we found $\approx 6500$ article pairs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common. As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in Figure \ref{toparticles}).

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
\caption{Histogram of Cluster Sizes (log scale).}
\label{clust}
\end{figure}
